A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-06-10 report_clean_final/TEX/numerics.tex
addede bruno's modifications

\section{Numerical Experiments}
This section is organized as follows. The first part is dedicated to the numerical implementation and simulation 
of the frequency domain formulation \eqref{vf1dcase}. We study the convergence of this formulation and the behaviour 
of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
performed with \urev{our} code written in Octave.  
We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with System (\ref{eq:simple_system}). 
We apply permutation to the above system 
to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm.

The intermediate part briefly validates the semi-lagrangian discretization of the time domain formulation.

The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of \mrev{the frequency   
and time domain codes }(computed for large values of time). 
The time-domain code implements the scheme described in \urev{Section \ref{sec:staggered_discretization}} and 
is written in Fortran.

@@

          \addplot[mark=*,cyan, mark size=1pt] table {pics_frequency_domain/data_airy/E2L2.dat};
        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L^{2}}$};  
        \addplot[dotted] table{pics_frequency_domain/data_airy/E_h2.dat};
         \addlegendentry{$O(h^2)$};
         \addplot[dashed] table{pics_frequency_domain/data_airy/H.dat};
         \addlegendentry{$O(h)$};
    \end{loglogaxis}
    \end{tikzpicture}
    \caption{Convergence rates for the \mrev{problem described in Section \ref{sec:airy_fd_validity} (the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy}))}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
    $E_{x}^{c}(x)=i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
    \label{fig:conv_rate}
\end{figure}
\subsubsection{Solution of the Frequency-Domain Problem with Resonance}
%\paragraph{Convergence}
Let us consider the case of the resonance, more precisely, we choose sufficiently smooth
$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
of Lemma \ref{lemma:well_posedness}  are satisfied. 
For simplicity, let us assume \mrev{that $\alpha(x)$ is smooth and }
\begin{align}
\label{eq:cond}
 \mrev{\alpha(x)=-x \text{  in some neighbourhood of $0$ }}.
\end{align}
\mrev{Let $h>0$ denote the meshwidth. }Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being respectively the exact and the numerical solution, }
we look for the ratio $h(\nu)$ that would ensure the bound on the absolute error 
\begin{align}
\label{eq:problem1}
\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}<\epsilon,
\end{align}
given a fixed value of $\epsilon>0$ and $\nu\rightarrow 0$. W.l.o.g. here we assume that $\nu>0$.

@@

\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}

@@

@@

 E_x^{\nu}(x)=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})}+S_{1}^{\nu}(x),

@@

where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$; $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
which, together with their derivatives, are bounded independently of $\nu$. 
\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ is available,  
based on the results of \cite{singular_solutions}. First of all, we
will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where 
the following expansion is valid \cite[Proposition 1]{singular_solutions}

@@

and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
 \|v-I^{h}v\|_{L^2}\leq Ch^2\left|v''\right|_{L^2},\; C>0,\\
 \|v-I^{h}v\|_{H^1}\leq Ch|v''|_{L^2},\; C>0, 

@@

in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonance:

@@

 \left|\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,

@@

Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
where for $\nu=0$ this function is singular, 
we obtain the following rough bound
\begin{align*}
 \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x-i\nu c|^2}dx\right)^{\frac{1}{2}}
 %\leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
 \leq \frac{C}{\sqrt{\nu}},\qquad G,G',C>0,
\end{align*}
for sufficiently small $\nu>0$.
}
To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we notice that it can be represented in the following form, 
for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(0,0)$:
\begin{align}
\label{eq:ex_eq1}
 \frac{d^2E_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\rho_{\nu}^{k}(x-X_{\nu})}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
\end{align}
Assuming again that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
we deduce that there exists $c>0$, s.t. for all sufficiently small $\nu$ 
\bealn
 \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
 % &=c\left.
 %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
 \leq C\nu^{-5},\; 
\eealn
where $C>0$ does not depend on $\nu$. Plugging this into (\ref{eq:final_est}) we obtain
\ben
 \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
\een
From this it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
\begin{align}
\label{eq:estimate_h}
 h=\alpha_{\epsilon}\nu^{\frac{7}{4}},
\end{align}
where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. 
This prediction is very severe and is due to the singular nature of the problem under consideration.

Let us check numerically whether this holds true. 
To do so, we conduct the  numerical experiment with parameters for Problem 
(\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. \mrev{Recall as well that $\theta=0$. }
\begin{table}[htb!]
\begin{tabular}{l|l}
Parameter & Value \\
\hline
$\alpha(x)$ & $\left\{\begin{array}{lr}
10, & x\leq -10,\\
-x, & -10<x\leq 5,\\
-5, & x>5.
\end{array}\right.$ \\
$\delta(x)$ & 
$\left\{\begin{array}{lr}
0, & x\leq -10,\\
-4/30x-4/3,& -10<x\leq 5,\\
-2, & x>5.
\end{array}\right.$ \\
$g^{inc}(-L)$ & $-2 \sqrt{2}i\exp(-22\sqrt{2}i)$\\
$\lambda$ & 
$\sqrt{10}$\\
$L$& 15\\
$H$ & 10 \\
\end{tabular}
\caption{The parameters for the problem with the resonance.}
\label{tab:parameters}
\end{table}
Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with \mrev{width $h$ and 
 absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
was typically 10-200 times finer, except when the computation was performed for very small values of $h$ when results were compared with results computed on twice finer meshes}), let 
\begin{align}
\label{eq:def_epsilon}
h_{\epsilon}=\sup\{h: \|E_{x}^{\nu,h'}-E_{x}^{\nu}\|<\epsilon \text{ for all } h'<h\}.
\end{align}
The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Fig.~\ref{fig:dependence}.
\begin{figure}
\begin{tabular}{cc}
\includegraphics[height=0.32\textwidth]{pics_frequency_domain/h_nu.pdf}
&
\includegraphics[height=0.32\textwidth]{pics_frequency_domain/res_sol.pdf}
\end{tabular}
\caption{We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
defined in Table \ref{tab:parameters}. In the left figure the \urev{dependence} of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
In the right figure we show the computed solutions for this problem (\urev{for brevity denoted by $E_{x,y}^{\nu}$}) for different values of $\nu$. }
\label{fig:dependence}
\end{figure}
We can see that Estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
\begin{remark}
It can be shown that $\|E^{\nu}_{x}\|_{L^2}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
and thus the relative error control
\bealn
 \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}}{\|E^{\nu}_{x}\|_{L^2}}\leq \epsilon
\eealn
 is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$, \mrev{$\beta_{\epsilon}>0$.}
\end{remark}

@@

With very basic simulation, we show that the numerical strategy 
based on co-localised semi-lagrangian discretization is valid even for the resonant 
case.
The numerical tests have been kept to a minimum since \arev{much more} is needed to fully validate
the concept.

The setting of the numerical results of figure \ref{fig:vasl}
is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
The \arev{peak} is the hybrid resonance, visible on $E_x$ and $u_x$.
The total energy $\mathcal E(t)$ is the physical energy. 
The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
singular nature of the \arev{resonance} is captured by this new scheme without any doubt.

\begin{figure}{h}
	\begin{center}
		\begin{tabular}{ccc}
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ey_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Hz_moit.eps} &
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ex_moit.eps}
			\\
			$E_y$ & $H_z$  & $E_x^\nu$ \\
			%\hline
			\hline
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/uy_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/normes_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/ux_moit.eps}
			\\      
			$u_y$ & $t\mapsto \mathcal E(t)$ & $u_x^\nu$  \\

@@

		\end{tabular}   \end{center}
		\caption{An antenna sends a time-harmonic wave on the left. The medium is propagative
			on the left and non propagative
			on the right. The resonance is visible on $E_x$ and $u_x$. The time of the simulation is $T=2000$. The number of cells
			is typically 10000 to reach convergence.}
		\label{fig:vasl}
	\end{figure}

>>>>

\section{Numerical Experiments}
This section is organized as follows. The first part is dedicated to the numerical implementation and simulation 
of the frequency domain formulation \eqref{vf1dcase}. We study the convergence of this formulation and the behaviour 
of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
performed with \urev{our} code written in Octave.  
We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with System (\ref{eq:simple_system}). 
We apply permutation to the above system 
to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm. 
The intermediate part briefly validates the semi-lagrangian discretization of the time domain formulation.
The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of \mrev{the frequency   
and time domain codes }(computed for large values of time). 
The time-domain code implements the scheme described in \urev{Section \ref{sec:staggered_discretization}} and 
is written in Fortran.

@@

          \addplot[mark=*,cyan, mark size=1pt] table {pics_frequency_domain/data_airy/E2L2.dat};
        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L^{2}}$};  
        \addplot[dotted] table{pics_frequency_domain/data_airy/E_h2.dat};
         \addlegendentry{$O(h^2)$};
         \addplot[dashed] table{pics_frequency_domain/data_airy/H.dat};
         \addlegendentry{$O(h)$};
    \end{loglogaxis}
    \end{tikzpicture}
    \caption{Convergence rates for the \mrev{problem described in Section \ref{sec:airy_fd_validity} (the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy}))}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
    $E_{x}^{c}(x)=i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
    \label{fig:conv_rate}
\end{figure}

\subsubsection{Solution of the Frequency-Domain Problem with Resonance}
%\paragraph{Convergence}
Let us consider the case of the resonance, more precisely, we choose sufficiently smooth
$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
of Lemma \ref{lemma:well_posedness}  are satisfied. 
For simplicity, let us assume \mrev{that $\alpha(x)$ is smooth and }
\begin{align}
\label{eq:cond}
 \mrev{\alpha(x)=-x \text{  in some neighbourhood of $0$ }}.
\end{align}
\mrev{Let $h>0$ denote the meshwidth. }Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being respectively the exact and the numerical solution, }
we look for the ratio $h(\nu)$ that would ensure the bound on the absolute error 
\begin{align}
\label{eq:problem1}
\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}<\epsilon,
\end{align}
given a fixed value of $\epsilon>0$ and $\nu\rightarrow 0$. Without loss of generality here we assume that $\nu>0$.

@@

@@

 \|v-I^{h}v\|_{L^2}\leq C_1h^2\left\|v''\right\|_{L^2},\; C_1>0,\\
 \|v-I^{h}v\|_{H^1}\leq C_2h\|v''\|_{L^2},\; C_2>0, 
\item \mrev{An explicit bound on $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}. 
First of all, we 
will assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where, 
for sufficiently small $\nu$, the following expansion is valid \cite[Proposition 1]{singular_solutions}

@@

 E_x^{\nu}(x)=\tilde{E}_x^{\nu}+S_{1}^{\nu}(x),\\
 \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})},

@@

where $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
which, together with their derivatives, are bounded independently of $\nu$ for all sufficiently small values of $\nu$; 
$\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$. 
}
\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{singular_solutions}. As before, we 
will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where,
for sufficiently small $\nu$, it holds \cite[Proposition 1]{singular_solutions}

@@

and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$ 
for all sufficiently small values of $\nu$.}

@@

in particular, the term $\tilde{E}_{y}^{\nu}$:

@@

 \left|\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,

@@

Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
where for $\nu=0$ $\left(E_{y}^{\nu}\right)''$ is singular,  
we obtain the following rough bound
\begin{align*}
 \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x-i\nu c|^2}dx\right)^{\frac{1}{2}}
 %\leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
 \leq \frac{C}{\sqrt{\nu}},\qquad G,G',C>0,
\end{align*}
for sufficiently small $\nu>0$.

To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$
comes from the singular part of $\tilde{E}_{x}^{\nu}$, whose second derivative can be represented in the following form, 
for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(x,\nu)=(0,0)$:
\begin{align}
\label{eq:ex_eq1}
 \frac{d^2\tilde{E}_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\left(\rho_{\nu}(x-X_{\nu})\right)^{k}}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
\end{align}
}
Then there exists $c>0$, s.t. for all sufficiently small $\nu$ 
\bealn
 \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
 % &=c\left.
 %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
 \leq C\nu^{-5},\; 
\eealn
where $C>0$ does not depend on $\nu$. Plugging this into (\ref{eq:final_est}) we obtain
\ben
 \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
\een
From this it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
\begin{align}
\label{eq:estimate_h}
 h=\alpha_{\epsilon}\nu^{\frac{7}{4}},
\end{align}
where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. 
This prediction is very severe and is due to the singular nature of the problem under consideration.

Let us check numerically whether this holds true. 
To do so, we conduct the  numerical experiment with parameters for Problem 
(\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. \mrev{Recall as well that $\theta=0$. }
\begin{table}[htb!]
\begin{tabular}{l|l}
Parameter & Value \\
\hline
$\alpha(x)$ & $\left\{\begin{array}{lr}
10, & x\leq -10,\\
-x, & -10<x\leq 5,\\
-5, & x>5.
\end{array}\right.$ \\
$\delta(x)$ & 
$\left\{\begin{array}{lr}
0, & x\leq -10,\\
-4/30x-4/3,& -10<x\leq 5,\\
-2, & x>5.
\end{array}\right.$ \\
$g^{inc}(-L)$ & $-2 \sqrt{2}i\exp(-22\sqrt{2}i)$\\
$\lambda$ & 
$\sqrt{10}$\\
$L$& 15\\
$H$ & 10 \\
\end{tabular}
\caption{The parameters for the problem with the resonance.}
\label{tab:parameters}
\end{table}
Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with \mrev{width $h$ and 
 absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
was typically 10-200 times finer, except when the computation was performed for very small values of $h$ when results were compared with results computed on twice finer meshes}), let 
\begin{align}
\label{eq:def_epsilon}
h_{\epsilon}=\sup\{h: \|E_{x}^{\nu,h'}-E_{x}^{\nu}\|<\epsilon \text{ for all } h'<h\}.
\end{align}
The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Fig.~\ref{fig:dependence}.
\begin{figure}
\begin{tabular}{cc}
\includegraphics[height=0.32\textwidth]{pics_frequency_domain/h_nu.pdf}
&
\includegraphics[height=0.32\textwidth]{pics_frequency_domain/res_sol.pdf}
\end{tabular}
\caption{We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
defined in Table \ref{tab:parameters}. In the left figure the \urev{dependence} of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
In the right figure we show the computed solutions for this problem (\urev{for brevity denoted by $E_{x,y}^{\nu}$}) for different values of $\nu$. }
\label{fig:dependence}
\end{figure}
We can see that Estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
\begin{remark}
It can be shown that $\|E^{\nu}_{x}\|_{L^2}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
and thus the relative error control
\bealn
 \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}}{\|E^{\nu}_{x}\|_{L^2}}\leq \epsilon
\eealn
 is ensured by choosing $h$ as \mrev{$\beta_{\epsilon}\nu^{\frac{3}{2}}$}, \mrev{$\beta_{\epsilon}>0$.}
\end{remark}

@@

With very basic simulation, we show that the numerical strategy 
based on co-localised semi-lagrangian discretization is valid even for the resonance.
The numerical tests have been kept to a minimum, and \arev{many more} are needed to fully validate
the concept.
The setting of the numerical results of Figure \ref{fig:vasl}
is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
The \arev{peak} is the hybrid resonance, visible on $E_x$ and $u_x$.
The total energy $\mathcal E(t)$ is the physical energy. 
The comparison with Figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
singular nature of the \arev{resonance} is captured by this new scheme without any doubt.

\urev{Notice that in this case we shifted the computational domain is shifted
for visualization purposes,
so that $L=0$ and the point where the resonance occurs is $x_h=20$.}

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{ccc}
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ey_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Hz_moit.eps} &
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ex_moit.eps}
			\\
			$x\mapsto E_y^\nu(T,x)$ & $  x\mapsto H_z^\nu(T,x)$  & $x\mapsto E_x^\nu(T,x)$ \\
			%\hline
			%\hline
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/uy_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/normes_moit.eps}
			&
			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/ux_moit.eps}
			\\      
			$x\mapsto u_y^\nu(T,x)$ & $t\mapsto \mathcal{E}^{\nu}(t)$ & $x\mapsto u_x^\nu(T,x)$  \\

@@

		\end{tabular}   \end{center}
		\caption{An antenna sends a time-harmonic wave on the left. The medium is propagative
			on the left and non-propagative
			on the right. The resonance is visible on the real functions
			$E_x^\nu$ and $u_x^\nu$. The time of the simulation $T=2000$ is chosen large enough so that the
			periodic solution is captured, at least numerically. The number of cells
			is typically 10000 to reach space  convergence. The shift for visualization purposes if $+20$, which explains
			why the resonance is now at $x=20$.}
		\label{fig:vasl}
	\end{figure}

### 2015-06-10 report_clean_final/TEX/proc.tex
addede bruno's modifications

\begin{document}
%%\newcommand{\urev}[1]{{\color{bluer}#1}}
%%\newcommand{\arev}[1]{{\color{red}#1}}
%%\newcommand{\mrev}[1]{{\color{greem}#1}}
%%color printing
\newcommand{\urev}[1]{{\color{black}#1}}
\newcommand{\arev}[1]{{\color{black}#1}}
\newcommand{\mrev}[1]{{\color{black}#1}}

@@

\input{timedomain}
\input{numerics}
\input{absorption}
\input{conclusions}

\begin{thebibliography}{99}
	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
	Handbook of mathematical functions
	\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{cedar}
Charles, F., Despr\'es, B., Mehrenberg, M., 
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.

@@

\bibitem{compfluids}
S. Del Pino, B. Despr\'es, P. Hav\'e, H. Jourdren, and P. F. Piserchia. 3D finite
volume simulation of acoustic waves in the earth atmosphere.
Comput. \&
Fluids, 38(4):765-777, 2009.

@@

@@

@@

\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
\bibitem{Eidus} Eidus. D.M. (1969). The principle of limit amplitude. Russian Mathematical Surveys, vol. 24, issue 3, 97-167.

@@

\bibitem{singular_solutions}
Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O. Singular solutions for the plasma at the resonance. 2014. $\langle$ hal-01097364$\rangle$

>>>>

\begin{document}
%\newcommand{\urev}[1]{%{\color{bluer}#1}   
\newcommand{\urev}[1]{#1}
%\newcommand{\arev}[1]{{\color{red}#1}}
\newcommand{\arev}[1]{#1}
%\newcommand{\mrev}[1]{{\color{greem}#1}}
\newcommand{\mrev}[1]{#1}
%%color printing
%\newcommand{\urev}[1]{{\color{black}#1}}
%\newcommand{\arev}[1]{{\color{black}#1}}
%\newcommand{\mrev}[1]{{\color{black}#1}}

@@

\input{timedomain}

\input{numerics}

\input{absorption}

\input{conclusions}

\begin{thebibliography}{99}

\bibitem{abramowitz_stegun} Abramowitz, M. and Stegun, I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
	Handbook of mathematical functions
\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.

\bibitem{cedar}
Charles, F., Despr\'es, B., Mehrenberg, M.  (2013).  
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal., 51(2), 840-863.

@@

\bibitem{compfluids}
Del Pino, S., Despr\'es, B., Hav\'e, P., Jourdren, H., and Piserchia, P. F. (2009). 3D finite
volume simulation of acoustic waves in the earth atmosphere.
Comput. \&
Fluids, 38(4):765-777.

@@

\bibitem{feix} Feix, M. R., Bertrand, P., and Ghizzo, A.  (1994). Eulerian codes for the Vlasov equation.  Series on Advances
in Mathematics for Applied Sciences 22, Kinetic Theory and Computing, pp. 45.

\bibitem{fifi} 
 Filbet, F., Sonnendrucker, E.  (2003). 
 Comparison of Eulerian Vlasov solvers,
Computer Physics Communications,
150, pp. 247-266

@@

\bibitem{guo}
Guo, W. and Qiu, J. - M. (2013). 
Hybrid semi-Lagrangian finite element-finite difference methods for the Vlasov
equation,
Journal of Computational Physics,
234, pp. 108-132.

@@

\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.

\bibitem{Eidus} Eidus, D.M. (1969). The principle of limit amplitude. Russian Mathematical Surveys, vol. 24, issue 3, 97-167.

\bibitem{soso}
Sonnendrucker, E., Roche, J., Bertrand, P., and A. Ghizzo (1998). 
The Semi-Lagrangian Method for the
Numerical Resolution of Vlasov Equations.
J. Comput. Phys.,
149, pp. 201-220.

@@

\bibitem{umeda}
Umeda, T., Nariyuki, Y. and Kariya, D. (2012).
A non-oscillatory and conservative semi-Lagrangian scheme with
fourth-degree polynomial interpolation for solving the Vlasov equation,
Computer Physics Communications,183, pp. 1094-1100.

\bibitem{singular_solutions}
Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O., 2014. Singular solutions for the plasma at the resonance. $\langle$ hal-01097364$\rangle$

### 2015-06-10 report_clean_final/TEX/resume.tex
addede bruno's modifications

La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma.
Il est en particulier d'int\'er\^et scientifique dans le cadre du d\'eveloppement  du projet ITER. Dans ce papier, nous nous concentrons sur des solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas magn\'etiques. Notre but est ici double. D'un c\^ot\'e nous 
approchons num\'eriquement la formulation fr\'equentielle \`a l'aide d'\'el\'ements finis,
 et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies. Nous comparons enfin num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
des principes d'amplitude et d'absorption limite.

>>>>

La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma.
Il est en particulier d'int\'er\^et scientifique dans le cadre du d\'eveloppement  du projet ITER. Dans ce papier, nous nous concentrons sur des solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas magn\'etiques. Notre but est ici triple. D'un c\^ot\'e nous 
approchons num\'eriquement la formulation fr\'equentielle \`a l'aide d'\'el\'ements finis,
 et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies. Finalement nous comparons  num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
des principes d'amplitude et d'absorption limite.
